simplified_likelihood

### 2023-05-02 inst/simplified_likelihood.Rmd
better idiom

```{r}
library("hyper2")
simplike <- function(n1,n2,n){
  H <- hyper3()
  H[c(p =1)] <- n2-2
  H[c(p1=1)] <- 1
  H[c(p2=1)] <- 1
  for(i in (n-n1+1):n)     { H[c(p1=1,p2=1,p=i)]  %<>% dec }
  for(i in (n-n2+2):(n-n1+1)){ H[c(p2=1,   p=i)]  %<>% dec }
  return(H)
} 
simplike(2,6,11)
simplike(1,6,11)
simplike(1,2,11)
```

>>>>

```{r}
library("hyper2")
simplike_lowlevel <- function(n1,n2,n,p1="p1",p2="p2",other="other"){
  stopifnot(n1<n2)
  H <- hyper3()
  H[setNames(1,other)] <- n2-2
  H[setNames(1,p1)] <- 1
  H[setNames(1,p2)] <- 1
  for(i in (n-n1+1):n){H[setNames(c(1,1,i),c(p1,p2,other))]  %<>% dec }
  for(i in (n-n2+2):(n-n1+1)){H[setNames(c(1,i),c(p2,other))] %<>% dec }
  return(H)
}

twodrivers <- function(...,n){ # twodrivers(ham=3, bottas=5,n=20)
  L <- list(...)
  stopifnot(length(L)==2)
  if(L[[1]] > L[[2]]){ # wrong way round
    tmp <- L[[2]]
    L[[2]] <- L[[1]]
    L[[1]] <- tmp
    names(L) <- rev(names(L))
  }
  simplike_lowlevel(as.numeric(L[[1]]),as.numeric(L[[2]]),n,names(L)[1],names(L)[2])
}

twodrivers(o=2,XX=6,n=11)
```

Now

```{r readtable}
a <- read.table("formula1_2019.txt")[1:2,1:21]
a
f <- function(i){
  jj <- as.list(a[,i])
  names(jj) <- rownames(a)
  return(jj)
}

H <- hyper3()
for(i in seq_len(ncol(a))){
  jj <- f(i)
  if(all(!is.na(as.numeric(unlist(jj))))){
    H <- H + do.call(twodrivers,c(jj,n=20))
  }
}
H
```

```{r maxh,cache=TRUE}
maxp(H)
```

```{r equaltest,cache=TRUE}
samep.test(H,c("Hamilton","Bottas"))
```
